\SW: Crowd-sourcing the Discovery of Gravitational Lenses

### 2014-07-29 doc/sw-system.tex
Added ROC curve

\subsection{Sample completeness and purity}
\label{sec:results:sample}

Rejection rate. Completeness and purity at P > retirement, P > 95\%, and 
as function of probability P. Compare stage 1 and stage 2.

Summarize performance at some fiducial threshold: eg P = 95\%.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

\subsection{Sample Properties}
\label{sec:results:sample}

We now quantify the performance of the \sw system in terms of the recovery of
the training set images. \Fref{fig:results:sample:roc} shows receiver
operating characteristic (ROC) curves for CFHTLS stage 1 and stage 2.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}
\centering\includegraphics[width=0.9\linewidth]{sw-system-figs/roc.png}
\caption{Receiver operating characteristic curves for the \sw system, using
the CFHTLS training set.}
\label{fig:results:sample:roc}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%  ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
